Extreme Value Chapter 3

### 2022-03-02 Ch3_samplesize/Figures_Ch3.Rmd
Pretty sure all figures are ready now.

Bias correction in GLM Lomax

@@

```{r fig.height=4, fig.width=12}

@@

>>>>

Bias correction

@@

```{r eval=FALSE, fig.height=6, fig.width=12}

@@

Nonparametric bootstrap correction for both the GLM Lomax and GP

```{r fig.width=10, fig.height=4}
dir_scenario <- "allinone_original"
load(paste0("Ch3_samplesize/", dir_scenario, "/allin1df.RData"))

# allin1df %>%
#   ggplot(., aes(x = factor(thresh_tests), y = log(gp_theta_hat/theta))) +
#   geom_hline(yintercept = 0, color = "red") +
#   geom_boxplot() -> a
# 
# allin1df %>%
#   ggplot(., aes(x = factor(thresh_tests), y = log(gp_theta_bar/theta))) +
#   geom_hline(yintercept = 0, color = "red") +
#   geom_boxplot() -> b
# 
# plot_grid(a,b, ncol = 2)
```

```{r Fig4, fig.width=12, fig.height=5}

allin1df %>%
  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
  mutate(original = log(gp_theta_hat/theta),
         corrected = log(gp_theta_bar/theta)) %>%
  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
  drop_na() %>%
  mutate(thresh_tests = factor(thresh_tests),
         samp_n_tests = factor(samp_n_tests)) %>% 
  mutate(labelsamp = paste("n =", samp_n_tests),
         labelsamp = factor(labelsamp, levels = c("n = 80", "n = 200", "n = 500", "n = 800", "n = 1000", "n = 1600"))) %>%
  ggplot(., aes(x = thresh_tests, y = theta_val, color = type, fill = type)) +
  facet_wrap(~labelsamp, nrow = 2) +
  geom_boxplot() +
  scale_color_manual(values = pal_mixture[c(1,4)], name = "Bias") +
  scale_fill_manual(values = pal_mixture[c(2,3)], name = "Bias") +
  geom_hline(yintercept = 0, color = "red") +
  labs(y = TeX(r'($log(\hat{\theta} / \theta)$)'), x = "Distance Level Estimated") +
  theme_bw()
ggsave("Ch3_samplesize/Figures/Figure4.png")
```

```{r Figure5, fig.width=12, fig.height=4}

i_threshold <- 50

allin1df %>%
  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
  mutate(original = log(gp_theta_hat/theta),
         corrected = log(gp_theta_bar/theta)) %>%
  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
  drop_na() %>%
  mutate(thresh_tests = factor(thresh_tests),
         samp_n_tests = factor(samp_n_tests)) -> readyplot_df

baseplot_fx <- function(i_threshold){readyplot_df %>% 
  filter(., thresh_tests == i_threshold) %>% 
  ggplot(., aes(x = samp_n_tests, y = theta_val, color = type, fill = samp_n_tests)) +
  # facet_wrap(~thresh_tests, scales = "free", ncol=4) +
  geom_boxplot() +
  scale_color_manual(values = c("black", "grey"), name = "Estimator") +
  scale_fill_manual(values = pal_sampsize, name = "Sample Size") +
  geom_hline(yintercept = 0, color = "red") +
  labs(y = "Theta ratio", subtitle = paste("Dist. level =", i_threshold)) +
  theme_bw() +
  theme(legend.position = "none",
        axis.title.x = element_blank())}

baseplot <- baseplot_fx(50) +
  theme(legend.position = "right",
        legend.box = "horizontal") +
  guides(fill = guide_legend(ncol = 2))

baselegend <- get_legend(baseplot)

# Distance level plots

t50 <- baseplot_fx(50)
t100 <- baseplot_fx(100)
t150 <- baseplot_fx(150)
t250 <- baseplot_fx(250)
t500 <- baseplot_fx(500)
t750 <- baseplot_fx(750)
t1000 <- baseplot_fx(1000)

toprow <- plot_grid(t50, t100, t150, t250, nrow = 1) 
bottomrow <- plot_grid(t500, t750, t1000, baselegend, nrow = 1)

plot_grid(toprow, bottomrow, nrow=2)
ggsave("Ch3_samplesize/Figures/Figure5.png")

```{r eval = FALSE, fig.width=12, fig.height=3}

allin1df %>%
  dplyr::select(., thresh_tests, samp_n_tests, lomax_theta_hat, lomax_theta_bar, theta) %>%
  mutate(original = lomax_theta_hat - log(theta),
         corrected = lomax_theta_bar - log(theta)) %>%
  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
  drop_na() %>%
  ggplot(., aes(x = factor(thresh_tests), y = theta_val, color = type)) +
  facet_wrap(~samp_n_tests, nrow = 1) +
  geom_boxplot() +
  geom_hline(yintercept = 0, color = "red") +
  theme_bw()
```

```{r eval=FALSE}

allin1df %>%
  dplyr::select(., thresh_tests, samp_n_tests, lomax_theta_hat, lomax_theta_bar, theta) %>%
  mutate(original = lomax_theta_hat,
         corrected = lomax_theta_bar) %>%
  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
  drop_na() %>%
  group_by(thresh_tests, samp_n_tests, type) %>%
  summarise(ExpVal_theta_hat = mean(theta_val),
            theta = log(mean(theta)),
            bias = ExpVal_theta_hat - theta) %>%
  ggplot(., aes(x = thresh_tests, y = bias, color = type)) +
  facet_wrap(~samp_n_tests) +
  geom_point() +
  theme_bw()

allin1df %>%
  dplyr::select(., thresh_tests, samp_n_tests, gp_theta_hat, gp_theta_bar, theta) %>%
  mutate(original = gp_theta_hat,
         corrected = gp_theta_bar) %>%
  pivot_longer(., cols = c(original, corrected), names_to = "type", values_to = "theta_val") %>%
  drop_na() %>%
  group_by(thresh_tests, samp_n_tests, type) %>%
  summarise(ExpVal_theta_hat = mean(theta_val),
            theta = mean(theta),
            bias = ExpVal_theta_hat - theta) %>%
  ggplot(., aes(x = thresh_tests, y = bias, color = type)) +
  facet_wrap(~samp_n_tests) +
  geom_point() +
  theme_bw()
